Descriptives and model description

### 2022-12-07 descriptives.qmd
add code for top 9 origin countries for plots

dem_longMissing <- dem_longMissing %>%
  mutate(children = rowSums(select(., female_0_4, female_5_11, female_12_17,
                            male_0_4, male_5_11, male_12_17)),
         childrenProp = children/total,
         femaleProp = female/total,
         )

>>>>

# Calculate the proportions of children and girls/women
dem_longMissing <- dem_longMissing %>%
  mutate(children = rowSums(select(., female_0_4, female_5_11, female_12_17,
                            male_0_4, male_5_11, male_12_17)),
         childrenProp = children/total,
         femaleProp = female/total,
         )

# Get the 9 largest origin_iso3 by total
top_origin_iso3 <- dem_longMissing %>%
  group_by(origin_iso3) %>%
  summarize(total = sum(total)) %>%
  arrange(desc(total)) %>%
  top_n(9)
